---
title: "Alcohol vs Seat choice"
author: "JudyInsunza"
date: "09/16/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


## Numerical Summarys 
```{r}
favstats(momheight~Sex,data=ucdavis1)
```
I noticed that the number of people sitting in the middle is the height (89) between the number of people sitting in the front (40)and the back (36). However, the standard deviation of the people sitting in the back is the highest (12580471) compared to the people sitting the front (3806013) and the middle

## Inferential Tests


```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

When looking at the P-value which was about 0.000116, I noticed that it is really small and telling me that there is a big statistical difference between the values. 

```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence level. I saw the confidence intervals of the Front-Back, Middle-Back and Middle-Front seats, with 0 indicating if the lines are significantly different, since 0 doesn't go through their confidence intervals. However, for the Middle-Front seats,0 does go through the confidence interval, and so indicating that there is no significant different between them.  
  

## Conclusions





